LAGOS lake depth

### 2020-03-13 figures/00_qa.Rmd
adjust figure dimensions
figure cleanup

```{r lgnemanual-vs-bathy-depth, fig.height=3}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

@@

gg_mean <- ggplot() +
  geom_point(data = dt_sub, 
             aes(x = bathymetry, y = combined, color = lake_state), 
             alpha = 0.6) +
  geom_point(data = dplyr::filter(dt_sub, !(lake_state %in% c("ME"))), 
             aes(x = bathymetry, y = combined, color = lake_state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Calculated (m)") + ylab("Reported (m)") +
  ggtitle("Mean Depth")

@@

cowplot::plot_grid(gg_max + theme(legend.position = "none"), 
                   gg_mean + theme(axis.title.y = element_blank()), 
                   rel_widths = c(0.7, 1))
```

>>>>

```{r lgnemanual-vs-bathy-depth, fig.height=2.5, fig.width=5.5}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

@@

gg_mean <- ggplot() +
  geom_point(data = dt_sub, 
             aes(x = bathymetry, y = combined, color = lake_state), 
             alpha = 0.6) +
  geom_point(data = dplyr::filter(dt_sub, !(lake_state %in% c("ME"))), 
             aes(x = bathymetry, y = combined, color = lake_state)) +
  geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Calculated (m)") + ylab("Reported (m)") +
  ggtitle("Mean Depth")

@@

cowplot::plot_grid(gg_max + cowplot::theme_cowplot() +
                     theme(legend.position = "none"), 
                   gg_mean + cowplot::theme_cowplot() + 
                     theme(axis.title.y = element_blank()), 
                   rel_widths = c(0.8, 1))
```
